Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-11 prop_letter.tex
prop_letter.tex \section{Quantum Measurements} Fix typos...

As an example, consider a three-dimensional Hilbert space with
orthonormal basis $\{\ket{0},\ket{1},\ket{2}\}$ and an observable $Q$
with spectral decomposition $\proj{1} + 2\,\proj{2} +
3\,\proj{3}$. Here are two fragments of valid probability measures
$\mu_1$ and $\mu_2$ that can associated with this space:
$\mu_1(\proj{0}) = 0.5$, $\mu_1(\proj{1}) = 0.5$,
$\mu_1(\proj{2}) = 0$, and $\mu_2(\proj{0}) = 0$,
$\mu_2(\proj{1}) = 0.5$, $\mu_2(\proj{2}) = 0.5$. By the Born rule,
the first probability measure corresponds to the quantum system being
in the state $1/\sqrt{2}(\ket{0}+\ket{1})$ and the second corresponds
to the quantum system being in the state
$1/\sqrt{2}(\ket{1}+\ket{2})$. The expectation value of the observable
is the first case is 1.5 and in the second it is 2.

>>>>

As an example, consider a three-dimensional Hilbert space with
orthonormal basis $\{\ket{0},\ket{1},\ket{2}\}$ and an observable $Q$
with spectral decomposition $\proj{0} + 2\,\proj{1} +
3\,\proj{2}$. Here are two fragments of valid probability measures
$\mu_1$ and $\mu_2$ that can associated with this space:
$\mu_1(\proj{0}) = 0.5$, $\mu_1(\proj{1}) = 0.5$,
$\mu_1(\proj{2}) = 0$, and $\mu_2(\proj{0}) = 0.5$,
$\mu_2(\proj{1}) = 0$, $\mu_2(\proj{2}) = 0.5$. By the Born rule,
the first probability measure corresponds to the quantum system being
in the state $(\ket{0}+\ket{1})/\sqrt{2}$ and the second corresponds
to the quantum system being in the state
$(\ket{0}+\ket{2})/\sqrt{2}$. The expectation value of the observable
is the first case is 1.5 and in the second it is 2.
